### 2016-02-23 paper.tex
Refine RM2 description in intro

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
that was designed to operate in a reach of the lower Mississippi River near
Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three blades,
a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R$, and a
preliminary analysis with Sandia's CACTUS vortex line numerical model
\cite{Murray2011} predicted a full-scale performance coefficient of 47\% at 1
m/s flow speed and a tip speed ratio $\lambda \equiv \frac{\omega R}{U_\infty} =
3.15$ \cite{Barone2011}, where $\omega$ and $R$ are the rotor's angular velocity
and radius, respectively. Note that the RM2 rotor solidity would be considered
moderate to high for a wind turbine, but MHK rotors are typically higher
solidity since they must withstand approximately an order of magnitude higher
torque in typical flows, necessitating relatively larger blades to meet strength
and fatigue life requirements.

>>>>

Reference Model 2 (RM2) is a dual-rotor, vertical-axis cross-flow river turbine
that was designed to operate in a reach of the lower Mississippi River near
Baton Rouge, Louisiana \cite{Barone2011, Neary2011}. The rotor has three tapered
blades and a relatively low solidity $Nc/(\pi D)$ or chord-to-radius ratio $c/R
\approx 0.1$. A preliminary analysis with Sandia's CACTUS vortex line numerical
model \cite{Murray2011} predicted an individual rotor's full-scale performance
coefficient to be 47\% at 1 m/s flow speed and a tip speed ratio $\lambda \equiv
\frac{\omega R}{U_\infty} = 3.15$ \cite{Barone2011}, where $\omega$ and $R$ are
the rotor's angular velocity and radius, respectively. Note that the RM2 rotor
solidity would be considered moderate to high for a wind turbine, but MHK rotors
are typically higher solidity since they must withstand approximately an order
of magnitude higher torque in typical flows, necessitating relatively larger
blades to meet strength and fatigue life requirements.
